Unimodular covers of 3-dimensional parallelepipeds and Cayley sums

### 2019-07-05 unimodular-covers.tex
making tikz figures

\begin{figure}[htb]
  \centering
\begin{tikzpicture}[mynode/.style={circle, inner sep=1.5pt, fill=red}, scale =
  .7]
%coordinate axes
   \tkzInit[xmax=3.5,ymax=3.5,xmin=-3.5,ymin=-3.5]
%        \tkzLabelX[orig=false,label options={font=\tiny}]
%        \tkzLabelY[orig=false,label options={font=\tiny}]
%        \tkzGrid
%        \tkzDrawX
%        \tkzDrawY

%edges b, t
  \node[mynode] (b1) at (-3,-2) {}; 
  \node[mynode] (b2) at (2, 0.2) {};  
  \node[mynode] (t1) at (-2.7, 1) {};  
  \node[mynode] (t2) at (1.6,0.7) {};  
  %\node[mynode] (E) at (-2,-1) {};  
  %\node[mynode] (F) at (-3,-3) {};

%p
  \node[mynode] (p1) at (0,-1) {}; 
  \node[mynode] (p2) at (0,1) {};

%q
  \node[mynode] (q1) at (-1,0) {}; 
  \node[mynode] (q2) at (1,0) {};

 % \draw[black] (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- (A);
  \draw[name path = b, black] (b1) -- (b2); 
  \draw[name path = t, black] (t1) -- (t2);
  \draw[name path = p, black, thick] (p1) -- (p2);
  \draw[name path = q, black, thick] (q1) -- (q2);

 \tkzDrawLine[add=0.2 and 0.3, color=black, dashed](b1, b2);
  \tkzDrawLine[ add=0.3 and 0.4, color=black, dashed](t1, t2);
  \path [name intersections={of = p and b}];
  \coordinate (S)  at (intersection-1);

>>>>

\begin{figure}[htb]
  \centering
\begin{tikzpicture}[mynode/.style={circle, inner sep=1.5pt, fill=red}, scale =
  1]
%coordinate axes
   \tkzInit[xmax=3.5,ymax=3.5,xmin=-3.5,ymin=-3.5]
%        \tkzLabelX[orig=false,label options={font=\tiny}]
%        \tkzLabelY[orig=false,label options={font=\tiny}]
%        \tkzGrid
%        \tkzDrawX
%        \tkzDrawY

%edges b, t
  \node[
%label={[shift={(0,-0.67)}]$b_1$}, 
mynode] (b1) at (-3,-2) {}; 
  \node[
%label={[shift={(0,-0.67)}]$b_2$}, 
mynode] (b2) at (2, 0.2) {};  
  \node[
%label={[shift={(0,0)}]$t_1$}, 
mynode] (t1) at (-2.7, 1) {};  
  \node[
%label={[shift={(0,0)}]$t_2$}, 
mynode] (t2) at (1.6,0.7) {};

  \draw[fill=gray!80, nearly transparent] (2.93,0.61) -- (0,0.81)  -- (0,-0.68) -- cycle;
  %\node[mynode] (E) at (-2,-1) {};  
  %\node[mynode] (F) at (-3,-3) {};

%p
  \node[
%label={[shift={(0,-0.67)}]$p_1$}, 
mynode] (p1) at (0,-1) {}; 
  \node[
%label={[shift={(0,0)}]$p_2$}, 
mynode] (p2) at (0,1) {};  
%  \node[{p}]  at (-0.3,0.95)

%q
  \node[
%label={[shift={(0,-0.67)}]$q_1$}, 
mynode] (q1) at (-1.7,-0.4) {}; 
  \node[
%label={[shift={(0,-0.67)}]$q_2$}, 
mynode] (q2) at (0.3,-0.4) {};

  \draw[ name path = b, black, thick] (b1) node[below, xshift=1.7cm, yshift=0.7cm] {b} -- (b2); 
  \draw[name path = t, black, thick] (t1) node[below, xshift=1.2cm, yshift=-0.1cm] {t} -- (t2);
  \draw[name path = p, black, thick] (p1) node[left, xshift=0 cm, yshift=1.3cm] {p} -- (p2);
  \draw[name path = q, black, thick] (q1) node[below, xshift=0.4cm, yshift=0cm] {q} -- (q2);

 \tkzDrawLine[add=0.2 and 0.3, color=black, dashed](b1, b2);
 \tkzDrawLine[ add=0.3 and 0.4, color=black, dashed](t1, t2);

  \tkzDefLine[orthogonal=through p1](p1,p2)
  \tkzDrawLine[add = 2 and 1,color=black, dashed](p1,tkzPointResult)

  \tkzDefLine[orthogonal=through p2](p1,p2)
  \tkzDrawLine[add = 2 and 1,color=black, dashed](p2,tkzPointResult)
